\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-12-01 public/paper/pyg4ometry.tex
Authorship
Remove colours from href links.

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{lineno}
\modulolinenumbers[5]
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}

@@

\hypersetup{
    colorlinks=false,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Pyg4ometry paper},
    bookmarks=true,
    pdfpagemode=FullScreen,
}

@@

\author[a]{S.T. Boogert\corref{author}}
\author[a]{A. Abramov}
\author[a]{L.J. Nevay}
\author[a]{W. Shields}
\author[a]{S.D. Walker}

@@

There are more complex extensions that can be considered for inclusion into \PYGEOMETRY{}.
The meshes created by \PYGEOMETRY{} are generally of very high quality and can be used for a
wide range of applications. An idea already being developed is the export of the geometry mesh data to
data formats used in augmented or virtual reality software to create interactive visualisations of MCRT
simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in
liquid noble dark matter detectors. ParaView/VTK are becoming standard software for complex 3D visualisation and
the ability to write geometry to formats readily loaded and manipulated by these programs will
significantly aid the presentation of geometry along with the results of MCRT simulations.

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage[hidelinks]{hyperref}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{lineno}
\modulolinenumbers[5]
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}

@@

%\hypersetup{
%    colorlinks=false,
%    linkcolor=blue,
%    filecolor=magenta,
%    urlcolor=cyan,
%    pdftitle={Pyg4ometry paper},
%    bookmarks=true,
%    pdfpagemode=FullScreen,
%}

@@

\author[a]{S.D. Walker}
\author[a]{A. Abramov}
\author[a]{L.J. Nevay}
\author[a]{W. Shields}
\author[a]{S.T. Boogert\corref{author}}

@@

There are more complex extensions that can be considered for inclusion into \PYGEOMETRY{}.
The meshes created by \PYGEOMETRY{} are generally of very high quality and can be used for a
wide range of applications. An idea already being developed is the export of the geometry mesh data to
data formats used in augmented or virtual reality software to create interactive visualisations of MCRT
simulations.  Triangular meshes also have applications for GPU-accelerated photon tracking in
optical photon based particle physics detectors. ParaView/VTK are becoming standard software for 
complex 3D visualisation and the ability to write geometry to formats readily loaded and manipulated 
by these programs will significantly aid the presentation of geometry along with the results of MCRT 
simulations.
